Universal Anonymous Signatures

### 2022-07-19 prism-backend/research/gsac/formal-uas.tex
Done with main pass after Markulf's comments.

        \procedure{$\OPEN(\oid,\Sig,\msg)$}{%
          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\Sig,\Yeval,\msg,\feval)
          \in \SIG[\uid] \\
          (\yinsp,\iproof) \gets
          \Open(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
          \pcif \CSIG[\Sig] \neq \bot: \\
          \pcind \textrm{Parse $\CSIG[\Sig]$ as $(\oid,\cuid_b,\scid_b,
            \Yeval,\msg,\feval$} \\          
          \hspace*{83pt}\cuid_{1-b},\cSig_{1-b},\scid_{1-b},
          \TYeval) \\
          \pcind (\tyinsp,\tiproof) \gets
          \Open(\PRVOK[\oid],\IK[\ISR[\scid]],\\
          \hspace*{107pt} \cSig_{1-b},\msg,\feval) \\
          \pcind \pcif \tyinsp \neq \yinsp: \pcreturn \bot \\
          \pcreturn (\yinsp,\iproof)
        }

@@

        \procedure{$\OBTCHALb(\cid,\cuid_{0,1},\iid,\attrs,\cscid_{0,1}=
          \lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]})$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
          \in \CRED: \\
          \pcind \pcreturn \bot \\
          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
          \pcif \fissue(\UK[\cuid_0],\cscid_0,\attrs) \neq
          \fissue(\UK[\cuid_1],\cscid_1,\attrs) \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\UK[\cuid_b],\PUBIK[\iid],\cscid_b,\attrs),\adv \rangle \\
          \CCRED[\ccid_b] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
          \pcreturn \top \\
        }

        \procedure{$\CHALb(\cuid_{0,1},\oid,\cscid_{0,1}=
          \lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]},\msg,\feval)$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\
          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\UK[\cuid_0],\cscid_0,
          \msg) \\
          \TYeval = (\tyeval^0,\tyeval^1) \gets
          \feval(\UK[\cuid_1],\cscid_1,\msg) \\
          \pcif \yeval^0 \neq \tyeval^0: \pcreturn \bot \\
          \pcif \Yeval \notin \rngfeval \lor \TYeval \notin \rngfeval:
          \pcreturn \bot \\          
          \cSig_b \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
          \hspace*{71pt}\cscid_b,\msg,\feval) \\
          \cSig_{1-b} \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
          \hspace*{80pt}\cscid_{1-b},\msg,\feval) \\          
          \CSIG[\cSig_b] \gets 
          \lbrace (\oid,\cuid_b,\cscid_b,\Yeval,\msg,\feval,\\
          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b},\TYeval)\rbrace \\
          \pcreturn \cSig_b
        }

@@

    \caption{Detailed oracles available in our model (2/2). Oracles for
      obtaining credentials, signatures, and processing them.}
    \label{fig:oracles2}
  \end{figure*}
}

@@

% Note that, for all the helper functions, in the case of credentials, transcripts,
% and signatures by honest users, it is enough to have access to the corresponding
% state information (described below) maintained by the challenger in our
% experiments. For credentials and join transcripts of corrupt users, or
% dishonestly produced signatures, we do need to perform actual extraction.
% Certainly, the challenger
% needs special knowledge/power such as decryption trapdoors, the ability to
% rewind the game, or program random oracles. The approach needs thus to depend on
% the concrete construction. \jdv{Although, for the case of \ExtractIssue and
%   \IdentifyUK, online extractability (or alternative requirements, such as
%   non-parallel or logarithmic number of joins) is necessary.}

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
    \textrm{\todo{This needs updating}} \\
    \parm \gets \Setup(1^\secpar) \\
    (\uid,\oid,\scid,\msg,\feval)
    \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS,\RREG}(\parm) \\
    \pcif \feval \notin \famfeval: \pcreturn 0 \\
    \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
    (\Sig = (\sig,\yeval)) \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,
    \feval) \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) = 0: \pcreturn 1 \\
    \pcfor \cid \in \scid \pcdo: \\
    \pcind \textrm{Let}~\scred^{\cid}~\textrm{be the credentials used to obtain}
    ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,\fissue^{\cid}),\cdot)\\
    \pcind \pcif \fissue^{\cid}(\UK[\uid],\scred^{\cid},\ATTR[\cid]) = 0: \pcreturn 1 \\
    (\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\scid,\msg) \\
    \pcif \yeval^0 \neq \yeval: \pcreturn 1 \\
    (\yinsp,\iproof) \gets \Open(\PRVOK[\gid],\PUBIK[\scid],\Sig,\msg,\feval) \\
    \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\yinsp,\iproof,\Sig,\msg,\feval)
    = 0~\lor \\
    \pcind \yinsp \neq \finsp^\gid((\yeval,\yeval^1),\UK[\uid],\scid,\msg)): \\
    \pcind \pcreturn 1 \\
    \pcreturn 0
  }  
  \caption{Correctness experiment for \UAS schemes.}
  \label{fig:exp-uas-corr}
\end{figure}

@@

\begin{figure}[htp!]
  \centering
  \scalebox{0.9}{
    \begin{minipage}[t]{0.57\textwidth}
      \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        \cid \gets \adv^{\Oforgeissue}(\parm) \\
        \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \\
        \pcind \pcreturn 0 \\
        % (\usk,\sCred) \gets \ExtractIssue(\trap,\trans[\cid]) \\
        ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]}) \\
        \hspace*{5em}\gets \ExtractIssue(\trap,\trans[\cid]) \\
        % \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
        % \trans[\cid_i]) \\
        % \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
        \pcif \fissue((\upk,\usk),\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
        \rbrace_{i\in[n]}) = 0: \\
        \pcind \pcreturn 1 \\
        \pcif \OWNR[\cid] \notin \HU \cup \CU: \pcreturn 1 \\
        \pcreturn 0
      }
    \end{minipage}
    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
        (\parm,\trap) \gets \Setup(1^\secpar) \\
        (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
        \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
        \SIG[\uid]: \pcreturn 0 \\
        \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
        \pcreturn 0 \\
        (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
        \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg,\feval)
        = 0: \pcreturn 1 \\
        % (\usk,\sCred,\tyeval^1,\yinsp') \gets
        % \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
        % \pcif \yinsp \neq \yinsp': \pcreturn 1 \\
        % \pcreturn 0
	((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},
        \yeval^1,\yinsp') \gets \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
        (\yeval^0,\yeval^1) \gets \feval((\upk,\usk),\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]}, \msg) \\
        \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
        \pcreturn 1 \\
        \pcif \finsp((\yeval^0,\yeval^1),(\upk,\usk),\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]},\msg)
        \neq \yinsp \lor \yinsp \neq \yinsp':
        \pcreturn 1 \\
        \pcif \OWNR[\scid] \notin \HU \cup \CU: \pcreturn 1 \\
        \pcreturn 0        
      }      
    \end{minipage}
  }
  \caption{Experiments for credential issuance and signature unforgeability in
    \UAS schemes.}
  \label{fig:exp-uas-unfor}
\end{figure}

@@

\begin{figure}[htp!]  
  \centering
  \scalebox{0.9}{
    \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
      (\parm,\trap) \gets \SimSetup(1^\secpar) \\
      (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval,\yinsp,\iproof) \gets
      \adv^{\Oframe}(\parm) \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
      \pcreturn 0 \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg) = 0:
      \pcreturn 0 \\
      ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},\tyeval^1,\yinsp') \gets
      \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
      % \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
      % \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1: \pcreturn 1 \\
      % \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
      % \lor \yinsp \neq \yinsp': \pcreturn 1 \\
      \Yeval=(\yeval^0,\yeval^1) \gets \feval((\upk,\usk),\lbrace (\cid_i,
      \attrs_i)\rbrace_i{i\in[n]}, \msg) \\
      \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
      \pcreturn 1 \\
      \pcif \finsp((\yeval^0,\yeval^1),(\upk,\usk),\lbrace(\cid_i,\attrs_i)
      \rbrace_{i\in[n]},\msg)
      \neq \yinsp \lor \yinsp \neq \yinsp': \\
      \pcind \pcreturn 1 \\
      \pcif \OWNR[\scid] \in \HU \land
      (\cdot,\cdot,\Sig,\Yeval,\msg,\feval) \notin \SIG[\OWNR[\scid]]: \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }
  }
  \caption{Experiment for non-frameability on \UAS schemes.}
  \label{fig:exp-uas-frame}
\end{figure}

@@

\paragraph{$\parm \gets \Setup(\secpar,\AttrSpace)$.} %
The setup process essentially generates the public parameters for all the
building blocks. It runs $\Cparm \gets \CSetup(\secpar)$, $\SBCMparm \gets
\SBCMSetup(\secpar)$, $\Sparm \gets \SSetup(\secpar)$, $\Eparm \gets
\ESetup(\secpar)$, $\NIZKcrs_{\Issue} \gets \NIZKSetup^{\NIZKRel_{\Issue}}
(\secpar)$, $\NIZKcrs_{\Sign} \gets \NIZKSetup^{\NIZKRel_{\Sign}}(\secpar)$, and
$\NIZKcrs_{\Open} \gets \NIZKSetup^{\NIZKRel_{\Open}}(\secpar)$. Return $
(\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},
\NIZKcrs_{\Open},\AttrSpace)$. % Many of these parameter setup algorithms can
% actually be run by separate entities. For simplicity of exposition, we bundle
% them together here.

@@

@@

In previous subsections, we have described a main construction for \CUASGen,
where generalization is achieved by allowing system designers to specify
concrete \fissue, \feval and \finsp functions depending on their needs. Note
however that alternative constructions are possible, that are close to \CUASGen,
but differ in key aspects while still meeting the \UAS model. We briefly
describe them next, as we leverage them to build related schemes. Security
proofs are deferred to \appref{app:uas-variants-proofs}

\paragraph{$\CUASGen^{prv-iss}$: Tweaking $\NIZKRel_{\Sign}$ for issuer
  privacy.} %
In \CUASGen, it is required that the identity of the issuer of each credential
used to produce a signature is revealed. This seems reasonable for usual
situations since, intuitively, it would seem hard for a verifier to accept a
signature produced with a credential without knowing if the issuer is
trustworthy. However, there may also be cases in which relaxations are
acceptable. For instance, it may be enough to know that the issuer belongs to
some set of well-known issuers. From a more theoretical point of view, this is
also interesting, as it allows to mimic ring signatures from \UAS constructions.
\todo{XXX}

\paragraph{$\CUASGen^{usr-iss}$: Collapsing issuers and users.} %
On occasions, it may be useful to not make a distinction between issuers and
users. For instance, for credential delegation, or in decentralized identity
systems. In both cases, users may end up acting as issuers themselves.
\todo{XXX}

>>>>

        \procedure{$\OPEN(\oid,\Sig,\msg)$}{%
          \textrm{Let}~\uid~\textrm{be s.t.}~(\cdot,\scid,\Sig,\Yeval,\cdot,
          \feval)
          \in \SIG[\uid] \\
          (\yinsp,\iproof) \gets
          \Open(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
          \pcif \CSIG[\Sig] \neq \bot: \\
          \pcind \textrm{Parse $\CSIG[\Sig]$ as $(\oid,\cuid_b,\scid_b,
            \Yeval,\msg,\feval$} \\          
          \hspace*{83pt}\cuid_{1-b},\cSig_{1-b},\scid_{1-b},
          \TYeval) \\
          \pcind (\tyinsp,\tiproof) \gets
          \Open(\PRVOK[\oid],\PUBIK[\scid],\\
          \hspace*{107pt} \cSig_{1-b},\msg,\feval) \\
          \pcind \pcif \tyinsp \neq \yinsp: \pcreturn \bot \\
          \pcreturn (\yinsp,\iproof)
        }

@@

        \procedure{$\OBTCHALb(\cid,\cuid_{0,1},\iid,\attrs,\cscid_{0,1}=$\\
          \hspace*{5.25em}$\lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]})$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
          \in \CRED: \\
          \pcind \pcreturn \bot \\
          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
          \pcif \fissue(\UK[\cuid_0],\cscid_0,\attrs) \neq
          \fissue(\UK[\cuid_1],\cscid_1,\attrs) \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\UK[\cuid_b],\PUBIK[\iid],\cscid_b,\attrs),\adv \rangle \\
          \CCRED[\ccid_b] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
          \pcreturn \top \\
        }

        \procedure{$\CHALb(\cuid_{0,1},\oid,\cscid_{0,1}=$\\
          \hspace*{5em}$\lbrace (\ccid_{0,i},\ccid_{1,i})
          \rbrace_{i\in[n]},\msg,\feval)$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \\
          \pcind \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\
          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\UK[\cuid_0],\cscid_0,
          \msg) \\
          \TYeval = (\tyeval^0,\tyeval^1) \gets
          \feval(\UK[\cuid_1],\cscid_1,\msg) \\
          \pcif \yeval^0 \neq \tyeval^0: \pcreturn \bot \\
          \pcif \Yeval \notin \rngfeval \lor \TYeval \notin \rngfeval:
          \pcreturn \bot \\          
          \cSig_b \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
          \hspace*{71pt}\cscid_b,\msg,\feval) \\
          \cSig_{1-b} \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
          \hspace*{80pt}\cscid_{1-b},\msg,\feval) \\          
          \CSIG[\cSig_b] \gets 
          \lbrace (\oid,\cuid_b,\cscid_b,\Yeval,\msg,\feval,\\
          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b},\TYeval)\rbrace \\
          \pcreturn \cSig_b
        }

@@

    \caption{Detailed oracles available in our model (2/2). Oracles for
      obtaining credentials, signatures, and processing them.
    \markulf{No concurrent issuing. \adv~is stateful.}}
    \label{fig:oracles2}
  \end{figure*}
}

@@

% Note that, for all the helper functions, in the case of credentials, transcripts,
% and signatures by honest users, it is enough to have access to the corresponding
% state information (described below) maintained by the challenger in our
% experiments. For credentials and join transcripts of corrupt users, or
% dishonestly produced signatures, we do need to perform actual extraction.
% Certainly, the challenger
% needs special knowledge/power such as decryption trapdoors, the ability to
% rewind the game, or program random oracles. The approach needs thus to depend on
% the concrete construction. \jesus{Although, for the case of \ExtractIssue and
%   \IdentifyUK, online extractability (or alternative requirements, such as
%   non-parallel or logarithmic number of joins) is necessary.}

@@

\begin{figure}[htp!]
  \centering
  \scalebox{0.9}{
    \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\uid,\oid,\scid,\msg,\feval)
      \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS,\RREG}(\parm) \\
      \pcif \feval \notin \famfeval: \pcreturn 0 \\
      \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
      (\Sig = (\sig,\yeval)) \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,
      \feval) \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) = 0: \pcreturn 1 \\
      \pcfor \cid \in \scid \pcdo: \\
      \pcind \textrm{Parse}~\CRED[\cid]~\textrm{as}~
      (\cdot,\cdot,\cdot,\attrs,n,\lbrace(\cid_i,\cdot)\rbrace_{i\in[n]}));
%      \pcind \textrm{Let}~\scid^{\cid}~\textrm{be the {\cid}s used to obtain}
%      ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,
%      \fissue^{\cid}),\cdot)\\
      \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot)\\
      \pcind \pcif \fissue(\UK[\uid],\attrs,
      (\lbrace(\cid_i,\ATTR[\cid_i])\rbrace_{i\in[n]})) = 0: \pcreturn 1 \\
      (\yeval^0,\yeval^1) \gets \feval(\UK[\uid],(\scid,\ATTR[\scid]),\msg) \\
      \pcif \yeval^0 \neq \yeval: \pcreturn 1 \\
      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\yinsp,\iproof,\Sig,\msg,\feval)
      = 0~\lor \\
      \pcind \yinsp \neq \finsp^\oid((\yeval,\yeval^1),
      \UK[\uid],(\scid,\ATTR[\scid]),\msg)): \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }
  }
  \caption{Correctness experiment for \UAS schemes.}
  \label{fig:exp-uas-corr}
\end{figure}

@@

\begin{figure}[htp!]
  \centering
  \scalebox{0.9}{
    \begin{minipage}[t]{\textwidth}
      \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
        \cid \gets \adv^{\Oforgeissue}(\parm) \\
        \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot:
        \pcreturn 0 \\
        % (\usk,\sCred) \gets \ExtractIssue(\trap,\trans[\cid]) \\
        ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]})
        \gets \ExtractIssue(\trap,\trans[\cid]) \\
        % \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
        % \trans[\cid_i]) \\
        % \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
        \pcif \fissue((\upk,\usk),\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
        \rbrace_{i\in[n]}) = 0:
        \pcreturn 1 \\
        \pcif \OWNR[\cid] \notin \HU \cup \CU: \pcreturn 1 \\
        \pcreturn 0
      }
      \vspace*{0.5em}

    % \end{minipage}    
    % \begin{minipage}[t]{\textwidth}
      \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
        (\parm,\trap) \gets \Setup(1^\secpar) \\
        (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
        \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
        \SIG[\uid]: \pcreturn 0 \\
        \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
        \pcreturn 0 \\
        (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
        \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg,\feval)
        = 0: \pcreturn 1 \\
        % (\usk,\sCred,\tyeval^1,\yinsp') \gets
        % \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
        % \pcif \yinsp \neq \yinsp': \pcreturn 1 \\
        % \pcreturn 0
	((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},
        \yeval^1,\yinsp') \gets \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
        (\yeval^0,\yeval^1) \gets \feval((\upk,\usk),\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]}, \msg) \\
        \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
        \pcreturn 1 \\
        \pcif \finsp((\yeval^0,\yeval^1),(\upk,\usk),\lbrace(\cid_i,\attrs_i)
        \rbrace_{i\in[n]},\msg)
        \neq \yinsp \lor \yinsp \neq \yinsp':
        \pcreturn 1 \\
%        \textrm{Let~}\scid \gets \lbrace \cid_i \rbrace_{i\in[n]};
        \pcif \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \notin \HU \cup \CU:
        \pcreturn 1 \\
        \pcreturn 0        
      }      
    \end{minipage}
  }
  \caption{Experiments for credential issuance and signature unforgeability in
    \UAS schemes.}
  \label{fig:exp-uas-unfor}
\end{figure}

@@

\begin{figure}[htp!]  
  \centering
  \scalebox{0.9}{
    \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
      (\parm,\trap) \gets \SimSetup(1^\secpar) \\
      (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval,\yinsp,\iproof) \gets
      \adv^{\Oframe}(\parm) \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
      \pcreturn 0 \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg) = 0:
      \pcreturn 0 \\
      ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},\tyeval^1,\yinsp') \gets
      \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
      % \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
      % \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1: \pcreturn 1 \\
      % \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
      % \lor \yinsp \neq \yinsp': \pcreturn 1 \\
      \Yeval=(\yeval^0,\yeval^1) \gets \feval((\upk,\usk),\lbrace (\cid_i,
      \attrs_i)\rbrace_i{i\in[n]}, \msg) \\
      \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
      \pcreturn 1 \\
      \pcif \finsp((\yeval^0,\yeval^1),(\upk,\usk),\lbrace(\cid_i,\attrs_i)
      \rbrace_{i\in[n]},\msg)
      \neq \yinsp \lor \yinsp \neq \yinsp': \\
      \pcind \pcreturn 1 \\
      \textrm{Let~}\scid \gets \lbrace \cid_i \rbrace_{i\in[n]};
      \pcif \OWNR[\scid] \in \HU \land
      (\cdot,\cdot,\Sig,\Yeval,\msg,\feval) \notin \SIG[\OWNR[\scid]]: \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }
  }
  \caption{Experiment for non-frameability on \UAS schemes.}
  \label{fig:exp-uas-frame}
\end{figure}

@@

\paragraph{$\parm \gets \Setup(\secpar)$.} %
The setup process essentially generates the public parameters for all the
building blocks. It runs $\Cparm \gets \CSetup(\secpar)$, $\SBCMparm \gets
\SBCMSetup(\secpar)$, $\Sparm \gets \SSetup(\secpar)$, $\Eparm \gets
\ESetup(\secpar)$, $\NIZKcrs_{\Issue} \gets \NIZKSetup^{\NIZKRel_{\Issue}}
(\secpar)$, $\NIZKcrs_{\Sign} \gets \NIZKSetup^{\NIZKRel_{\Sign}}(\secpar)$, and
$\NIZKcrs_{\Open} \gets \NIZKSetup^{\NIZKRel_{\Open}}(\secpar)$. Return $
(\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},
\NIZKcrs_{\Open})$. % Many of these parameter setup algorithms can
% actually be run by separate entities. For simplicity of exposition, we bundle
% them together here.

@@

\markulf{Put proofs here for XXXX?}\jesus{I can't parse XXXX.}

@@

In previous subsections, we have described a main construction for \CUASGen,
where generalization is achieved by allowing system designers to specify
concrete \fissue, \feval and \finsp functions depending on their needs. Note
however that alternative constructions are possible, that are close to \CUASGen,
but differ in key aspects while still meeting the \UAS model. We briefly
describe them next, as we leverage them to build related schemes. \todo{Security
proofs are deferred to \appref{app:uas-variants-proofs}.}

\paragraph{$\CUASGen^{usr-iss}$: Collapsing issuers and users.} %
On occasions, it may be useful to not make a distinction between issuers and
users. For instance, for credential delegation, or in decentralized identity
systems. In both cases, users may end up acting as issuers themselves. The
algorithms are as in \CUASGen, except that there is no \UKeyGen -- or, rather,
the steps run by \UKeyGen are exactly the same as in \IKeyGen. Concretely,
$\usk \gets \isk$ and $\upk \gets \ipk$, where \isk and \ipk are generated
as in \IKeyGen.

\paragraph{$\CUASGen^{hide-iss}$: $\NIZKRel_{\Sign}$ with issuer hiding.} %
In \CUASGen and $\CUASGen^{usr-iss}$, it is required that the identity of the
issuer of each credential involved in a signature is revealed. This seems
reasonable for usual situations since, intuitively, it seems hard that a
verifier accepts a signature produced with a credential without knowing if the
credential's issuer is trustworthy. However, there may be cases in which
relaxations are acceptable. For instance, it may be enough to know that the
issuer belongs to some set of well-known issuers. We merge this with the
previous extension that collapses issuers and users. Although it would also be
possible to apply the modification to \CUASGen independently, from a theoretical
point of view, the combined extension interesting, as it allows to mimic ring
signatures.

We show the modified NIZK relation for signing in \figref{fig:nizk-ring}. For
notational simplicity, we restrict to just one credential per signature.
%
Modelling-wise, no changes are needed. Perhaps notably, in this case, the
anonymity property is still required to enforce that both challenge signatures
are associated to the same set of (potential) issuers -- otherwise, it is
trivial to distinguish signatures.

\begin{figure}[ht!]
  \scalebox{0.9}{
    \input{figures/nizk-ring.tex}
  }
  \caption{$\NIZKRel^{hide-iss}_{\Sign}$ relation for $\CUASGen^{hide-iss}$.}
  \label{fig:nizk-ring}
\end{figure}

### 2022-07-19 prism-backend/research/gsac/introduction-paper.tex
Done with main pass after Markulf's comments.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{
    \input{figures/relations.tex}
  }
  \caption{Summary of schemes that can be instantiated as restrictions of our
    generic construction, \CUASGen, and proved secure under our \UAS model.
    $\CUASGen^{\ast}$ denotes that minor changes to the basic construction
    beyond the concrete $(\fissue,\feval,\finsp)$-restrictions are needed.
    Between parenthesis we show the adopted reference model, and the section
    offering full detail.
  }
  \label{fig:relations}
\end{figure}

>>>>

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{
    \input{figures/relations.tex}
  }
  \caption{Summary of schemes that can be instantiated as restrictions of our
    generic constructions, $\CUASGen^{\ast}$, and proved secure under our \UAS
    model. Between parenthesis we show the adopted reference model, and the
    section offering full detail.}
  \label{fig:relations}
\end{figure}
